\documentclass[10pt]{article}
\usepackage[top=1in, bottom=1in, left=0.5in, right=0.5in]{geometry}
\usepackage{parskip}
\usepackage{hyperref}
\usepackage{enumitem}
\pagestyle{empty}
\setlength\parindent{0pt}
\def \boxwidth {6in}
\newcommand{\cvsec}[2]{
	\begin{tabular}[t]{ p{1in} p{6in} }
		\sc{#1} & 
		    \begin{tabular}[t]{@{}p{\boxwidth}@{}}
                #2
            \end{tabular}
	\end{tabular}
	\vspace{0.15in}
}
\begin{document}

{\Large \noindent Emma Tosch}\\
\rule{\linewidth}{0.3mm}\\

\cvsec{Contact \newline Information}{
	\begin{tabular}[t]{@{}p{3.75in}r@{}}
		231 Elm Street 2R & 140 Governors Drive\\
		Northampton, MA 01060 & Amherst, MA 01002\\
		\url{etosch@fastmail.fm} & \url{etosch@cs.umass.edu}\\
	 	& \url{http://github.com/etosch}\\
	 	& \url{http://blogs.umass.edu/etosch}\\
                &   PhD Advisor: Emery Berger
	\end{tabular}
}
	 
\cvsec{Education}{
        Ph.D. {\bf Computer Science}. University of Massachusetts, Amherst. Amherst, MA. 2011 -- present.  \\
        M.S. {\bf Computer Science}. University of Massachusetts Amherst. Amherst, MA. 2011 -- 2015.\\
        M.A. {\bf Computer Science}. Brandeis University. Waltham, MA. 2009 -- 2011. \\
	B.A. {\bf English Literature}. Wellesley College. Wellesley, MA. 2006 -- 2008.
}

\cvsec{Research \newline Experience}{
{\bf Research Intern}. June 2015 -- August 2015. Facebook, Inc. Menlo Park, CA. Core Data Science -- Economic Research Team, Mentor: Eytan Bakshy. Static Analysis for the PlanOut DSL. \\\\
		{\bf Research Assistant}. June 2013 -- present. University of Massachusetts, Amherst. PLASMA Lab, Advisor : Emery Berger. Developing a domain specific programming language and runtime system
to design, debug, and deploy scientific surveys on the web, at scale.\\\\
		{\bf Research Assistant}. September 2011 -- January 2013. University of Massachusetts, Amherst. CI Lab, Advisor : Lee Spector. Researched new metrics for evaluating parameters of evolutionary
search based on techniques from nonparametric statistics.\\\\
		{\bf Visiting Researcher}. June 2010 -- August 2010. Institute for Creative Technologies. Playa Vista, CA. Supervisor : Ron Artstein. Augmented and evaluated a natural language generation and
question-answering system for virtual humans.
}

\cvsec{Publications}{
        E. Tosch, E. Berger. SurveyMan: Programming and Debugging Surveys at Scale. \emph{Proceedings of the 2014 ACM International Conference on Object Oriented Programming Systems Languages and Applications}. ACM New York, NY, USA. 2014. {\bf Best Paper Award.}\\\\
        E. Tosch, E. Berger. Programming and Debugging Surveys. POPL OBT 2014.\\\\
		E. Tosch, L. Spector. Achieving COSMOS: A metric for determining when to give up and when to reach for the stars. \emph{Proceedings of the 14th Intl. Conf. on Genetic and Evolutionary Computation Conference Companion}. ACM New York, NY, USA. 2012.\\\\
	K. Harrington, E. Tosch, L. Spector, J. Pollack. Compositional Autoconstructive Dynamics \emph{Proc. of the 8th Intl. Conf. on Complex Systems}. 2011.\\\\
	G. Chen, E. Tosch, R. Artstein, A. Leuski, D. Traum. Evaluating Conversational Characters Created through Question Generation. FLAIRS Conference. 2011.
}

\cvsec{Teaching \newline Experience}{
{\bf Mentor}. Google Summer of Code. Official mentor for a GSoC student (Prakhar Srivastav) working on a SurveyMan graphical interface. Summer 2015.\\
        {\bf Mentor}. UMass Amherst. Mentoring an undergraduate (Molly McMahon) for an independent study with Emery Berger. Spring 2014.\\
		{\bf  Teaching Assistant}. Reasoning Under Uncertainty (Undergraduate), University of Massachusetts, Amherst. Prof. Andrew McGregor. Spring 2013.\\
		{\bf Teaching Assistant, Guest Lecturer}. Intro. to Theory of Computation (Undergraduate), Brandeis University. Antonella DiLillo. Spring 2011.\\
		{\bf Teaching Assistant}. Structure and Interpretation of Computer Programs (Undergraduate), Brandeis University. Prof. Harry Mairson. Fall 2010.\\
		{\bf Teaching Assistant}. Data Structures (Undergraduate), Brandeis University. Antonella DiLillo. Spring 2010.\\
		{\bf Volunteer}. Cahners Computer Place, Museum of Science, Boston. Oct. 2009 -- May 2010, Sep. 2010 -- May 2011
}

\cvsec{%Relevant \newline
 Work \newline Experience}{
  {\bf Software Engineering Intern}. Sept. 2014 -- Dec. 2014. Google, Inc. Mountain View, CA.\\
  {\bf Data Warehouse Analyst}. March 2008 -- May 2009. Recombinant Data Corp. Newton, MA.\\
%  {\bf Usher}. September 2006 -- May 2008. American Repertory Theater. Cambridge, MA.\\ % comment this out later
  {\bf Assistant Loan Processor}. June 2005 -- October 2006. Hoffman Companies. Brookline, MA.\\
%  {\bf Clerk}. May 2006 -- August 2006. Lulu's Bakery. Boston, MA.\\ % comment this out later
%  {\bf Laborer}. January 2006 -- May 2006. Natick Community Organic Farm. Natick, MA.\\ % comment this out later
  {\bf Intern}. June 2004 -- August 2004. New Jersey Division of Law and Public Service. Trenton, NJ.\\
%  {\bf Clerk}. June 2002 -- April 2003. Wawa (Convenience Store). Hamilton, NJ.\\ % comment this out later



\cvsec{Talks and \newline Presentations}{
    \emph{Programming and Debugging Surveys}.\\
    \begin{tabular}{l}
    13 May 2015. Google, Inc. Invited Talk. Cambridge, MA.\\
    9 April 2015. Center for Data Science launch symposium. Poster session. Amherst, MA.\\
    22 October 2014. OOPSLA 2014. Oral Presentation (full). Portland, OR.\\
    11 June 2014. PLDI Student Research Competition. Poster session \& short talk. Edinburgh, Scotland.\\
    11 April 2014. CRA-W Graduate Cohort Workshop. Poster session. Santa Clara, CA.\\
    12 March 2014. UMass CS Women. Oral presentation. Amherst, MA.\\
    31 January 2014. Google PhD Summit. Lightning talk. Cambridge, MA.\\
    25 January 2014. POPL OBT Workshop. Oral presentation (full). San Diego, CA.\\
    \end{tabular}\\\\    
    
    \emph{Achieving COSMOS}.\\
    \begin{tabular}{l}
    7 July 2012. GECCO UP Workshop. Oral presentation (full). Philadelphia, PA.
    \end{tabular}\\\\
    
    \emph{Women in Computing}.\\
    \begin{tabular}{l}
    	24 April 2015. MassMutual Women in Technology Conference. \emph{Inspiring Women in Technology} Panelist.
    \end{tabular}
}


\cvsec{Professional \newline Activities}{
		CICS Graduate Representative. January 2016 -- present.
		UMass CS Women. Treasurer. January 2016 -- present, Co-Chair. January 2015 -- January 2016.\\
		Program Comittee Member. ECOOP DSLDI Workshop 2016. \\
		Artifact Evaluation Reviewer. PLDI 2016. \\
		NCWIT Aspirations Scholarship Reviewer. November 2014. \\
                Artifact Evaluation Committee. Reviewer. POPL 2015.\\
                Student Volunteer, SPLASH 2014. October 2014.\\
		Graduate Employee Organization, UAW 2322. Steward. September 2011 -- May 2014.\\
		NSF REU Graduate Student Mentor. Summer 2013.\\
		Oregon Programming Languages Summer School. Attendee. July -- August 2013.	\\
		Brandeis University Women in Computing (for Undergraduates). Founder. April 2010 -- May 2011. 
}


\cvsec{Honors, \newline Scholarships, \newline and Awards}{
2015 NCWIT Symantec Student Seed Funding (for UMass CS Women)\\
2015 UMass Amherst School of Computer Science Outstanding Synthesis Award\\
2014 OOPSLA Best Paper Award\\
2014 PLDI ACM Student Research Competition (1st Place)\\
2013 Future of Software Engineering Symposium Scholarship at Microsoft Research\\
2013 Programming Languages Mentoring Workshop Scholarship\\
2012 ACM-W conference scholarship (attended SIG-EVO)\\
2010 Grace Hopper Celebration of Women in Computing Scholarship\\
2005 Humanities Foundation Award in English Literature\\
}

\end{document}
